A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-08 4_method.tex
rewrite single bead segments section > printing order section

\paragraph{Single bead segments}
\Cref{single_bead_strategy}
We round to ingteger multiples of half the nozzle width so as to allow single-bead segments.
These could be printed from polygon and return to polygon over same segment without extruding.
See \cref{single_bead_strategy}.

We only introduce single bead segments along marked areas of the medial axis.
We could also do it for non-marked areas, but that would result in a small single bead segment at \emph{every} corner.

\hl{How to deal with single beads connecting two polys?}
: Print 1st poly $\to$ print single bead $\to$ print 2nd poly $\to$ travel over single bead $\to$ print 1st poly

\hl{How to deal with three-way intersection single beads?}
: Cut up in 1 single bead connecting two polys and 1 normal single bead only connected to one poly

Where to put the middle of the toolpath, based on the middle of the line, the line width and the processing order?

Idea: generate only outer 3 walls, except in marked regions where the distance $R < 5 \win$, so as to prevent jagged infill lines.
Don't generate transitions when $R > 5\win$ or something?
Only do this in skin regions?

>>>>

\paragraph{Printing order}
The order in which beads are printed has influence on the quality and dimensional accuracy of a print.
If the inner beads are printed first then small inaccuracies in the deposition process propagate outward and the final outline of the print layer will be less accurate.
However, if the second bead is printed before the outer bead then the outer bead has more material to adhere to, which lessens the overhang constraints.
We therefore choose to print the inner beads first starting from the second bead and at the very end print the outermost bead.

When all extrusion segments are generated, we combine them into semi-continuous polyline toolpaths.
These polylines generally form closed polygons, but at significant regions of the VQ the toolpaths consist of single bead polyline toolpaths.
See \cref{single_bead_strategy}.
These single bead polylines can connect to polygonal toolpaths and they can also meet each other at 3-way junctions.
We determine the printing order for all segments of a given bead index by minimizing the travel distance using a greedy path order optimizer.
\todo{[implementation needed!]}

In general the toolpath location should be centered on the middle of the bead.
However, when the bead width is smaller than the nozzle size we might want to offset the toolpath toward a previously printed bead.
That way the previously printed bead occludes part of the hole in the nozzle such that the unoccluded hole is as wide as the required bead width.
The printing order and the toolpath positioning of the beading strategy are therefore interrelated.

Around 3-way junctions we need to prevent overextrusion.
We need to reduce the extrusion amount after the first time we pass an intersection: commonly known as \emph{ghosting}.
See \cref{ghosting}.
In order to realize the reduction we remove a section from the extrusion bead up to a distance equal to the feature radius from the junction.

\begin{figure}
\centering
\includegraphics[width=.99\columnwidth]{sources/method/ghosting.pdf}
\caption{Ghosting prevents over-extrusion at junctions.}
\label{ghosting}
\end{figure}
